Title Goes Here

### 2020-03-03 analysis/paper/paper.Rmd
added here function

#need to figure out how to read the file inside the project
landmarks <- read.tps("/Users/gayoungp/CTtps/analysis/data/raw_data/A_BG_2.tps")

@@

#Compare multiple artifacts 
#Open multiple tps files 
#This will need to be changed to read files inside the project
datadir <- "/Users/gayoungp/CTtps/analysis/data/raw_data/"
files <- dir(datadir, pattern = "*.tps")

>>>>

#need to figure out how to read the file inside the project
landmarks <- read.tps(here("analysis/data/raw_data/A_BG_2.tps"))

@@

#Compare multiple artifacts 
#Open multiple tps files 
#This will need to be changed to read files inside the project
datadir <- here("/analysis/data/raw_data/")
files <- dir(datadir, pattern = "*.tps")
